Exploitation Techniques and Mitigations

### 2016-01-26 docs/paper.tex
Paper: Draft that damn abstract

% \maketitle
%
% \section*{Abstract}
% \label{sec:abstract}
%
% \setcounter{tocdepth}{1}
% \tableofcontents
%
% \newpage

>>>>

\maketitle

\section*{Abstract}
\label{sec:abstract}

\begin{quote}
    When a buffer overwrites a pointer\dots\enspace The story of a restless
    mind.
\end{quote}

Exploiting binaries is an extremely broad topic with many specialized
techniques for even the most exotic scenarios. In this writeup we will take a
look at exploiting \texttt{printf} with crafted format strings first and follow
up with an introduction about buffer overflows. Mitigation mechanisms will be
disabled at first and enabled one by one discussing them when they are put into
place. The buffer overflow will be augmented to inject and execute shell code
which is then prevented by the Data Execution Prevention (DEP) mechanism.

Return Oriented Programming (ROP) is introduced together with ret2libc to
circumvent DEP. Address Space Layout Randomization (ASLR) is presented next as
counter to ROP but is quickly broken with an information leak. StackGuard is a
more sophisticated mechanism against ROP but not a silver bullet and can be
easily brute forced in certain scenarios. Control-Flow Integrity (CFI) together
with a word about Stack Integrity is provided as an outlook for the reader.

Some basic knowledge about the target platform (x86) is communicated before
running the first exploit, but we take a quick glance at other architectures
(x86\_64 and ARM) before concluding this writeup.

\setcounter{tocdepth}{1}
\tableofcontents
